Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2016-10-05 writeup/local_pca_paper.tex
added author summary

>>>>

\section*{Author Summary}

How individuals of a species in different parts of the world are related to
each other is shaped by the history of migration and gene flow.  However,
natural selection affects some parts of the genome in different ways than
others: for instance, regions with more genes are more strongly affected by
deleterious mutations. In this paper we develop a visualization method to see
how patterns of mean relatedness vary along the genome, and aim to identify the
underlying biological cause. In three species: Medicago truncatula, Drosophila
melanogaster, and modern humans, we find significant heterogeneity in patterns
of relatedness along the genome that is correlated with genome structure. For
humans and Drosophila, this variation is closely connected to polymorphic
chromosomal inversions, while for Medicago, and for Drosophila once inversions
are removed, the variation is correlated with local gene density, and is
perhaps due to linked selection.
